Analysis of split plot design using MCMCglmm

### 2018-04-09 README.Rmd
Update study description in README.Rmd

The goal of _rice.awd.pests_ is to examine the effects of using alternate
wetting and drying irrigation techniques on insect populations and sheath blight
disease in rice paddies.

>>>>

The goal of _rice.awd.pests_ is to examine the effects of using alternate
wetting and drying irrigation techniques on sheath blight disease in rice
paddies.
